\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\LARGE Kaleb Kohn} \\
    \textit{Software Developer Intern}
\end{center}

\begin{center}
    \href{mailto:Kohnkaleb@gmail.com}{Kohnkaleb@gmail.com} $\vert$ 920-319-9209 $\vert$ \href{https://www.linkedin.com/in/kalebkohn}{LinkedIn: Kaleb Kohn}
\end{center}

\section*{Education}
\textbf{University of Wisconsin-Madison} \\
\textit{Madison, WI} \\
Bachelor of Arts (B.A) in Computer Science Candidate \\
(Expected graduation May 2025) \\
GPA: 3.76

\section*{Experience}
\textbf{Associate Software Developer} \\
\textit{Sentry Insurance, Madison, WI} \\
June 2022 – Present
\begin{itemize}[leftmargin=*]
    \item Automated webpage with Spring MVC, saving the company 700+ hours of work per year.
    \item Enhanced Query Performance with New Technology, improving efficiency and speed.
    \item Replaced SOAP with REST endpoints, implementing a lightweight solution to boost scalability and maintainability.
    \item Code Quality Improvements: Eliminated 800 code smells and reduced cognitive complexity in 60+ methods.
\end{itemize}

\textbf{Maintenance Management Analyst} \\
\textit{United States Air Force, Madison, WI} \\
Apr 2019 – Present
\begin{itemize}[leftmargin=*]
    \item Monitors, collects, assembles, and audits data for reports and briefings.
    \item Initiates special studies and investigations, and performs statistical analysis.
    \item Reports findings to managers with recommendations; informs managers of significant factors affecting the mission.
    \item Manages and operates Maintenance Information System (MIS) and performs functional system administrator (FSA) duties.
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item Command line program to find the shortest path between deployed military bases in the Middle East.
    \item Interactive adventure game for children.
    \item Chess opening practice application.
\end{itemize}

\section*{Languages/Technologies}
\begin{itemize}[leftmargin=*]
    \item Java (Proficient), Python (Proficient), JavaScript (Familiar), HTML (Familiar), CSS (Familiar), Spring MVC, Django, MySQL, jQuery
\end{itemize}

\end{document}